Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-10-26 ms.tex
Revising discussion of incomplete residue theorem treatment - putting disclaimer first

To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$. In this limit, $J_{\rm bc} \approx \sqrt{3} H_0$. We evaluate Eq. \ref{eq:Jbc} at $r=R$ and solve for the Fourier coefficients, $A(s)$. These are then used in Eq. \ref{eq:Hbc} to find $H_{\rm bc}(R, \sigma)$. Dividing by the contribution from $H_0$, we obtain the proportionality
\be \label{eq:hbc_scaling}
\frac{H_{\rm bc}(R, \sigma)}{H_0(R, \sigma)} \propto \frac{1}{(a\tau_0)^{1/3}}.
\ee
At large $\tau_0$, it is expected that the correction term will be small, but it will become increasingly important as $\tau_0$ decreases.

@@

Let us define the damping rate to be $\gamma \equiv i\omega$, which is real and positive for damped solutions. At the eigenvalues $\gamma=\gamma_{nm}$, the response $J(n, \sigma, \omega)$ is resonant. Near these $\gamma_{nm}$ poles, the eigenfunctions will have the form 
\be \label{eq:jnsigmaomega_approx}
J(n,\sigma,-i\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma_{nm} - \gamma} + {\rm terms\ which\ vary\ slowly\ in\ \gamma}.
\ee
for which an application of the residue theorem gives
\be
J_{nm}(r,\sigma,t) & \simeq & j_0(\kappa_n r) J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\ee
Summing over all spatial modes $n$ and over all eigenmodes $m$ for a given $n$, we obtain
\be \label{eq:Jrsigmat}
J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_{m=1}^{\infty} J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\ee
This ansatz captures the contributions from $n \times m$ simple poles, which seems to agree with Monte Carlo results for $x_s=0$ based on numerical calculations of this result. However, the analysis presented in Appendix \ref{app:wkb} suggests the ansatz is incomplete in the case where $x_s \neq 0$ and the spectrum is asymmetric.

>>>>

% Phil's edit:
To estimate the scaling of $H_{\rm bc}$ with $\tau_0$, a change of variables to $\bar{\sigma} =  \sigma/\tau_0$ and $\bar{s}=s \tau_0$ is used in Equations 16 and 17. In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find

%% TODO: Exclude this entirely or incorporate with Phil's edit?
%To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$. In this limit, $J_{\rm bc} \approx \sqrt{3} H_0$ from Eq. \ref{eq:bc2}. We evaluate Eq. \ref{eq:Jbc} at $r=R$ and solve for the Fourier coefficients, $A(s)$. These are then used in Eq. \ref{eq:Hbc} to find $H_{\rm bc}(R, \sigma)$. Dividing by the contribution from $H_0$, we obtain the proportionality
\be \label{eq:hbc_scaling}
\frac{H_{\rm bc}(R, \sigma)}{H_0(R, \sigma)} \propto \frac{1}{(a\tau_0)^{1/3}}.
\ee
At large $\tau_0$, it is expected that the correction term will be small, but it will become increasingly important as $\tau_0$ decreases.

@@

We now employ an ansatz that agrees with Monte Carlo results for $x_s=0$ based on numerical calculations of this result. However, the analysis presented in Appendix \ref{app:wkb} suggests the ansatz is incomplete in the case where $x_s \neq 0$ and the solution is asymmetric about the line center. Let us define the damping rate to be $\gamma \equiv i\omega$, which is real and positive for damped solutions. At the eigenvalues $\gamma=\gamma_{nm}$, the response $J(n, \sigma, \omega)$ is resonant. Near these $\gamma_{nm}$ poles, the eigenfunctions will have the form 
\be \label{eq:jnsigmaomega_approx}
J(n,\sigma,-i\gamma) & \simeq \frac{ J_{nm}(\sigma) }{\gamma_{nm} - \gamma} + {\rm terms\ which\ vary\ slowly\ in\ \gamma}.
\ee
for which an application of the residue theorem gives
\be
J_{nm}(r,\sigma,t) & \simeq & j_0(\kappa_n r) J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\ee
Summing over all spatial modes $n$ and over all eigenmodes $m$ for a given $n$, we obtain
\be \label{eq:Jrsigmat}
J(r,\sigma,t) & = & \sum_{n=1}^\infty j_0(\kappa_n r)  \sum_{m=1}^{\infty} J_{nm}(\sigma) e^{-\gamma_{nm}t}.
\ee
This ansatz captures only the contributions from $n \times m$ simple poles, and does not contain the asymmetric piece of the solution for $\sigma_s \neq 0$.
